quollr: An R Package for Visualizing \(2-\text{D}\) Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-05-08 paper-quollr.Rmd
Updated

```{r, echo=TRUE}
ggplot() + 
  geom_hexgrid(
    data = hb_obj$centroids, 
    aes(x = c_x, y = c_y)
    ) +
  coord_fixed()
```

@@

```{r, echo=TRUE}
ggplot() + 
  geom_trimesh(
    data = hb_obj$centroids, 
    aes(x = c_x, y = c_y)
    ) +
  coord_fixed()
```

@@

```{r, echo=TRUE}
df_exe <- comb_data_model(
  highd_data = scurve, 
  model_highd = df_bin, 
  model_2d = df_bin_centroids
  )

@@

```{r, echo=TRUE}
show_langevitour(
  point_data = df_exe, 
  edge_data = trimesh
  )
```

>>>>

```{r, echo=TRUE}
ggplot() + 
  geom_hexgrid(
    data = hb_obj$centroids, 
    aes(x = c_x, y = c_y)
    ) 
```

@@

```{r, echo=TRUE}
ggplot() + 
  geom_trimesh(
    data = hb_obj$centroids, 
    aes(x = c_x, y = c_y)
    ) 
```

@@

```{r, echo=TRUE, eval=FALSE}
df_exe <- comb_data_model(
  highd_data = scurve, 
  model_highd = df_bin, 
  model_2d = df_bin_centroids
  )

@@

```{r, echo=TRUE, eval=FALSE}
show_langevitour(
  point_data = df_exe, 
  edge_data = trimesh
  )
```

### 2025-05-08 paper-quollr.tex
Updated

#> # A tibble: 324 x 6
#>     from    to x_from  y_from  x_to   y_to
#>    <int> <int>  <dbl>   <dbl> <dbl>  <dbl>
#>  1    16    26 0.275   0.127  0.233 0.199 
#>  2    25    26 0.150   0.199  0.233 0.199 
#>  3    25    37 0.150   0.199  0.191 0.271 
#>  4    36    49 0.108   0.271  0.150 0.343 
#>  5    36    37 0.108   0.271  0.191 0.271 
#>  6     1     7 0.358  -0.0171 0.316 0.0550
#>  7    48    49 0.0665  0.343  0.150 0.343 
#>  8    37    38 0.191   0.271  0.275 0.271 
#>  9    26    27 0.233   0.199  0.316 0.199 
#> 10    27    38 0.316   0.199  0.275 0.271 

@@

\begin{verbatim}
#> # A tibble: 324 x 6
#>     from    to x_from  y_from  x_to   y_to
#>    <int> <int>  <dbl>   <dbl> <dbl>  <dbl>
#>  1    16    26 0.275   0.127  0.233 0.199 
#>  2    25    26 0.150   0.199  0.233 0.199 
#>  3    25    37 0.150   0.199  0.191 0.271 
#>  4    36    49 0.108   0.271  0.150 0.343 
#>  5    36    37 0.108   0.271  0.191 0.271 
#>  6     1     7 0.358  -0.0171 0.316 0.0550
#>  7    48    49 0.0665  0.343  0.150 0.343 
#>  8    37    38 0.191   0.271  0.275 0.271 
#>  9    26    27 0.233   0.199  0.316 0.199 
#> 10    27    38 0.316   0.199  0.275 0.271 
#> # i 314 more rows
\end{verbatim}

@@

\begin{verbatim}
augment(
  highd_data = scurve, 
  model_2d = df_bin_centroids, 
  model_highd = df_bin
  )
\end{verbatim}

@@

\begin{verbatim}
ggplot() + 
  geom_hexgrid(
    data = hb_obj$centroids, 
    aes(x = c_x, y = c_y)
    ) +
  coord_fixed()
\end{verbatim}

@@

\begin{verbatim}
df_exe <- comb_data_mode(
  highd_data = scurve, 
  model_highd = scurve_model_obj$model_highd, 
  model_2d = scurve_model_obj$model_2d
  )
\end{verbatim}

\begin{verbatim}
show_langevitour(
  point_df, 
  edge_df
  )
\end{verbatim}

@@

\begin{verbatim}
show_link_plots(
  point_df = df_exe, 
  edge_df = distance_small_df
  )
\end{verbatim}

\begin{verbatim}
show_error_link_plots(
  point_df = df_exe, 
  edge_df = distance_small_df
  )
\end{verbatim}

>>>>

#> # A tibble: 324 x 8
#>     from    to x_from  y_from  x_to   y_to from_count to_count
#>    <int> <int>  <dbl>   <dbl> <dbl>  <dbl>      <dbl>    <dbl>
#>  1    50    65 0.275   0.127  0.233 0.199          65       67
#>  2    64    65 0.150   0.199  0.233 0.199          39       67
#>  3    64    79 0.150   0.199  0.191 0.271          39       62
#>  4    78    94 0.108   0.271  0.150 0.343          62       34
#>  5    78    79 0.108   0.271  0.191 0.271          62       62
#>  6    21    36 0.358  -0.0171 0.316 0.0550         12       42
#>  7    93    94 0.0665  0.343  0.150 0.343          45       34
#>  8    79    80 0.191   0.271  0.275 0.271          62       68
#>  9    65    66 0.233   0.199  0.316 0.199          67       56
#> 10    66    80 0.316   0.199  0.275 0.271          56       68

@@

\begin{verbatim}
#> # A tibble: 670 x 8
#>     from    to  x_from  y_from    x_to    y_to from_count to_count
#>    <int> <int>   <dbl>   <dbl>   <dbl>   <dbl>      <dbl>    <dbl>
#>  1     1     2 -0.1    -0.0892 -0.0167 -0.0892          0        0
#>  2    16    17 -0.0584 -0.0171  0.0249 -0.0171          0        0
#>  3     1    31 -0.1    -0.0892 -0.1     0.0550          0        0
#>  4    16    32 -0.0584 -0.0171 -0.0167  0.0550          0        0
#>  5     3    17  0.0665 -0.0892  0.0249 -0.0171          0        0
#>  6    17    18  0.0249 -0.0171  0.108  -0.0171          0        0
#>  7    17    33  0.0249 -0.0171  0.0665  0.0550          0        0
#>  8    31    46 -0.1     0.0550 -0.0584  0.127           0        0
#>  9    32    47 -0.0167  0.0550  0.0249  0.127           0        0
#> 10    32    33 -0.0167  0.0550  0.0665  0.0550          0        0
#> # i 660 more rows
\end{verbatim}

@@

\begin{verbatim}
model_error <- augment(
  highd_data = scurve, 
  model_2d = df_bin_centroids, 
  model_highd = df_bin
  )

model_error
\end{verbatim}

@@

\begin{verbatim}
ggplot() + 
  geom_hexgrid(
    data = hb_obj$centroids, 
    aes(x = c_x, y = c_y)
    ) 
\end{verbatim}

@@

\begin{verbatim}
df_exe <- comb_data_model(
  highd_data = scurve, 
  model_highd = df_bin, 
  model_2d = df_bin_centroids
  )

df_exe
\end{verbatim}

\begin{verbatim}
show_langevitour(
  point_data = df_exe, 
  edge_data = trimesh
  )
\end{verbatim}

@@

\begin{verbatim}
df_exe <- comb_all_data_model(
  highd_data = scurve, 
  nldr_data = scurve_umap, 
  model_highd = df_bin, 
  model_2d = df_bin_centroids
  )
\end{verbatim}

\begin{verbatim}
show_link_plots(
  point_data = df_exe, 
  edge_data = trimesh
  )
\end{verbatim}

\begin{verbatim}
df_exe <- comb_all_data_model_error(
  highd_data = scurve, 
  nldr_data = scurve_umap, 
  model_highd = df_bin, 
  model_2d = df_bin_centroids, 
  error_data = model_error
  )
\end{verbatim}

\begin{verbatim}
show_error_link_plots(
  point_data = df_exe, 
  edge_data = trimesh
  )
\end{verbatim}
